\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE Cheung Sze Long, Karso} \\ \vspace{2pt}
    \begin{multicols}{2}
    \begin{flushleft}
    \href{https://github.com/Karso2023}{Github : https://github.com/Karso2023}\\
    \href{linkedin.com/in/karso-cheung-394428312}{Linkedin : linkedin.com/in/karso-cheung-394428312}
    \end{flushleft}
    
    \begin{flushright}
    %\href{https://karso2023.com}{To do: my personal site}\\
    \href{mailto:karsoo2023@gmail.com}{karsoo2023@gmail.com}
    \end{flushright}
    \end{multicols}
\end{center}

%-----------Education-----------
\vspace{-2pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southampton}{Sep. 2023 -- Present}
      {BSc Computer Science}{}
  \resumeSubHeadingListEnd

%-----------Experience-----------
\section{Experience}

\resumeSubHeadingListStart
    \resumeSubheading
      {Internship at Wuxi Boton}{11 Jul 2023 -- 25 Aug 2023}
      {Black-Box Tester in the Product Research and Development Department}{WuXi, China}
      \resumeItemListStart
        \resumeItem{Performed black-box testing to identify and report software defects.}
        \resumeItem{Authored a user manual in simplified Chinese.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Participant in RoboHack Hackathon}{May 2024}
      {}{University of Southampton}
      \resumeItemListStart
        \resumeItem{Collaborated in a team of four to develop a Python-based robotic car.}
        \resumeItem{Engineered the robot to successfully navigate a complex obstacle course.}
        \resumeItem{Achieved 4th place among 16 teams.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Startup Challenge}{Nov 2023}
      {Participant}{University of Southampton}
      \resumeItemListStart
        \resumeItem{Developed an initial prototype of a fashion app within 24 hours.}
        \resumeItem{Created and delivered a PowerPoint presentation to demonstrate the app's functionality.}
      \resumeItemListEnd
\resumeSubHeadingListEnd 

\vspace{10mm}

%-----------Projects-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeSubheading
      {TetrECS Game Development (University Project)}{Apr 2024}
      {Developer}{University of Southampton}
      \resumeItemListStart
        \resumeItem{Developed a fast-paced block placement game using JavaFX.}
        \resumeItem{Implemented game logic for piece placement, line clearing, and score calculation.}
        \resumeItem{Designed and built the user interface with custom components, graphics, and animations.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Chinese Soup E-commerce Website}{Dec 2022 -- May 2023}
      {Website Designer}{Southampton, England}
      \resumeItemListStart
        \resumeItem{Developed a website for Kinman, a startup company selling Chinese soup, using SquareSpace.}
        \resumeItem{Collaborated with the startup's founder to design and implement the site's layout, ensuring a user-friendly interface.}
        \resumeItem{Integrated e-commerce functionalities to facilitate online sales and transactions.}
        \resumeItem{Optimized the website for search engines to increase online visibility and traffic.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Technical Skills, Language Skills, and Interests-----------
\section{Technical Skills, Language Skills, and Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{OS:} Windows \\
    \textbf{Programming Languages:} Confident in Java; have previous experience in Python and C. \\
    \textbf{Software and Tools:} IntelliJ (IDE for coding), Rodin (for Event-B), DataGrip (for SQLite), Squarespace (with SEO optimization and content editing experience) \\
    \textbf{Version Control:} Git \\
    \textbf{Writing:} \LaTeX, Office \\
    \textbf{Languages:} Cantonese (native), Mandarin (fluent), English (fluent) \\
    \textbf{Interests:} Snooker (member of the university snooker team), Bowling, Golf, Badminton, Reading about Chinese history, Wiki editing, Travelling
    }}
 \end{itemize}

\end{document}
