\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\LARGE Sze Long Cheung, Karso} \\ \vspace{2pt}
    \begin{multicols}{2}
    \begin{flushleft}
    \href{linkedin.com/in/karso-cheung-394428312}{Linkedin: linkedin.com/in/karso-cheung-394428312}
    \end{flushleft}

    \begin{flushleft}
    \href{}{}
    \end{flushleft}
    
    \begin{flushright}
    %\href{https://karso2023.com}{To do: my personal site}\\
    \href{mailto:karsoo2023@gmail.com}{karsoo2023@gmail.com}
    \end{flushright}
    \end{multicols}
\end{center}

%-----------Education-----------
\vspace{-2pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southampton}{Sep. 2023 -- 2026}
      {BSc Computer Science}{}
      \vspace{-5pt}
      \begin{itemize}[leftmargin=*, label={}]
      \vspace{5pt}
        \item Modules include:
          \begin{itemize}[leftmargin=*, label={}]
            \item \textbf{1st Year:}
              \begin{itemize}[leftmargin=*, label={}]
                \item \textbf{Semester 1:} Foundation of Computer Science, Programming I, Professional Development, Computer Systems
                \item \textbf{Semester 2:} Algorithmics, Data Management, Programming II, Software Modelling
              \end{itemize}
            \item \textbf{2nd Year:}
              \begin{itemize}[leftmargin=*, label={}]
                \item \textbf{Semester 1:} Theory of Computing, Intelligent Systems, Programming III, Interaction Design
                \item \textbf{Semester 2:} Principles of Cyber Security, Distributed Systems \& Networks, Programming Language Concepts, Software Engineering Group Project
              \end{itemize}
          \end{itemize}
      \end{itemize}
  \resumeSubHeadingListEnd


%-----------Experience-----------
\section{Experience}

\resumeSubHeadingListStart
    \resumeSubheading
      {Hack The Box University CTF 2024: Binary Badlands}{Dec 2024}
      {Participant}{University of Southampton}
      \resumeItemListStart
        \resumeItem{Solved CTF questions related to forensics and reversing.}
        \resumeItem{Attempted CTF questions related to blockchain security}
        \resumeItem{Achieved 200th place among 1128 teams.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Advent of Cyber 2024}{Dec 2024}
      {Participant}{TryHackMe}
      \resumeItemListStart
        \resumeItem{Participated and solved CTF questions in Advant of Cyber 2024}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {RoboHack Hackathon}{May 2024}
      {Participant}{University of Southampton}
      \resumeItemListStart
        \resumeItem{Collaborated on a team of four to develop a Python-based robotic car.}
        \resumeItem{Engineered the robot to successfully navigate a complex obstacle course.}
        \resumeItem{Achieved 2nd place among 16 teams.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Startup Challenge}{Nov 2023}
      {Participant}{University of Southampton}
      \resumeItemListStart
        \resumeItem{Developed an initial prototype of a fashion app within 24 hours.}
        \resumeItem{Created and delivered a PowerPoint presentation to demonstrate the app's functionality.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Web designer at Kinman}{Dec 2022 -- May 2023}
      {Website Designer}{Southampton, England}
      \resumeItemListStart
        \resumeItem{Developed an e-commerce website for Kinman, a startup company selling Chinese soup, using SquareSpace.}
        \resumeItem{Collaborated with the startup's founder to design and implement the site's layout, ensuring a user-friendly interface.}
        \resumeItem{Integrated E-commerce functionalities to facilitate online sales and transactions.}
        \resumeItem{Optimised the website for search engines to increase online visibility and traffic.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Internship at Wuxi Boton}{11 Jul 2023 -- 25 Aug 2023}
      {Black-box Tester in the Product Research and Development Department}{WuXi, China}
      \resumeItemListStart
        \resumeItem{Performed black-box testing to identify and report software defects.}
        \resumeItem{Authored a user manual in simplified Chinese.}
        \resumeItem{Collaborated with individuals from various departments, which has enhanced my ability to work effectively with people from diverse backgrounds.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{10mm}

%-----------Projects-----------
\section{Projects}

\resumeSubHeadingListStart
    \resumeSubheading
      {Data analysis project}{Dec 2024}
      {}{}
      \resumeItemListStart
        \resumeItem{Walmart Sales Data Analysis with MySQL}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Responsive website}{July 2024}
      {Developer}{Hong Kong}
      \resumeItemListStart
        \resumeItem{Developed a responsive website using HTML, CSS and JavaScript.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {TetrECS Game Development}{Apr 2024}
      {Developer}{University of Southampton}
      \resumeItemListStart
        \resumeItem{Developed a fast-paced block placement game using JavaFX.}
        \resumeItem{Implemented game logic for piece placement, line clearing, and score calculation.}
        \resumeItem{Designed and built the user interface with custom components, graphics, and animations.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
    \resumeSubheading
      {Data analysis project}{Apr 2024}
      {}{University of Southampton}
      \resumeItemListStart
        \resumeItem{Created a SQLite database to represent current COVID-19 data}
        \resumeItem{Used GnuPlot to produce a graph representing the top 10 countries in terms of overall cumulative deaths.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
%-----------Technical Skills, Language Skills, and Interests-----------
\section{Technical Skills, Language Skills, and Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{OS:} Windows, Linux \\ \vspace{5pt}
    \textbf{Programming Languages:} Java, Python; have previous experience in SQL; understand the basics of Haskell \\ \vspace{5pt}
    \textbf{Markup Languages:} Have previous experience in HTML and CSS \\ \vspace{3pt}
    \textbf{Software and Tools:} IntelliJ, Visual Studio Code, Kali Linux, MySQL, Burp Suite, Ghidra, Excel \\ \vspace{5pt}
    \textbf{Version Control:} Git \\ \vspace{5pt}
    \textbf{Writing:} \LaTeX, Office \\ \vspace{5pt}
    \textbf{Languages:} Cantonese (native), Mandarin (fluent), English (fluent) \\ \vspace{5pt}
    \textbf{Interests:} Cybersecurity Capture the Flags (CTF) enthusiast and active member of the university's Cyber Security Society, Snooker (university team member), Chinese history, travelling
    }}
\end{itemize}


\end{document}
